\sysfull

### 2017-08-09 paper/evaluation.tex
added compile time

>>>>

We also evaluated the compile time for automatic task generation. The result are in Table~\ref{table:compile_time}.
Most of the compile time was due to pointer aliasing. We could not compile DFT application since it was using
builtins for math functions that weren't provided by Clang MSP430 backend.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Bitcount & Cold chain & Cuckoo & RSA & AR & Sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & > 1 \\
		\hline
	\end{tabular}
	\caption{Compile time in seconds.}
\label{table:compile_time}
\end{table}
